quollr: An R Package for Visualizing 2-D Models from Non-linear Dimension Reductions in High Dimensional Space

### 2025-05-12 paper-quollr.Rmd
Added intro to application

@@

The question is whether this accurately represents the cluster structure in the data. Our method can help here, and also help to provide a better \gD{} layout, as needed.

<https://www.nature.com/articles/s41586-018-0590-4#data-availability> <!--paper-->
<https://figshare.com/articles/dataset/Robject_files_for_tissues_processed_by_Seurat/5821263/1> <!--data-->

>>>>

Single-cell RNA sequencing (scRNA-seq) is a popular and powerful technology that allows you to profile the whole transcriptome of a large number of individual cells [@andrews2021].

@@

Limb muscle cells of mice in @tabula2018 are examined. There are $1067$ single cells, with $14997$ gene expressions. Following their pre-processing, tSNE was performed using ten principal components. @fig-NLDR-variety (a) is the reproduction of the published plot, with colour indicating the clustering results overlaid on the NLDR layout.The question is whether this accurately represents the cluster structure in the data. Our method can help here, and also help to provide a better $2-\text{D}$ layout, as needed.

<!-- https://www.nature.com/articles/s41586-018-0590-4#data-availability -->
<!-- https://figshare.com/articles/dataset/Robject_files_for_tissues_processed_by_Seurat/5821263/1 -->

### 2025-05-12 paper-quollr.tex
Added intro to application

Need to find another application

\url{https://www.nature.com/articles/s41586-018-0590-4\#data-availability}
\url{https://figshare.com/articles/dataset/Robject_files_for_tissues_processed_by_Seurat/5821263/1}

>>>>

Single-cell RNA sequencing (scRNA-seq) is a popular and powerful technology that allows you to profile the whole transcriptome of a large number of individual cells \citep{andrews2021}.

Clustering of single-cell data is used to identify groups of cells with similar expression profiles. NLDR often used to summarise the discovered clusters, and help to understand the results. The purpose of this example is to \emph{illustrate how to use our method to help decide on an appropriate NLDR layout that accurately represents the data}.

Limb muscle cells of mice in \citet{tabula2018} are examined. There are \(1067\) single cells, with \(14997\) gene expressions. Following their pre-processing, tSNE was performed using ten principal components. \citet{fig-NLDR-variety} (a) is the reproduction of the published plot, with colour indicating the clustering results overlaid on the NLDR layout.The question is whether this accurately represents the cluster structure in the data. Our method can help here, and also help to provide a better \(2-\text{D}\) layout, as needed.
